Eye-tracking

### 2019-04-19 childes/childes_entropy.Rmd
more plots for Monday

bootstrap entropy slopes
```{r slope bootstrapping}

>>>>

```{r make plots for joint lab meeting}
df <- prov_utterances %>%
  extract_stem_tokens(role = "adult", min_length = 5, max_length = 9)

prov_child_tokens <- extract_stem_tokens("child", 5, 9, prov_utterances) 
prov_adult_tokens <- extract_stem_tokens("not child",5, 9, prov_utterances)

prov_child_entropies <-  map_df(c(5,7,9), ~unigram_entropy(.x, prov_child_tokens)) %>%
  mutate(language = "English", person = "Child")
prov_adult_entropies <-  map_df(c(5,7,9), ~unigram_entropy(.x, prov_adult_tokens)) %>%
  mutate(language = "English", person = "Adult")

prov_entropies <- prov_child_entropies %>%
  bind_rows(prov_adult_entropies)

prov_entropies %>% ggplot(aes(x = word_order, y = empirical_entropy, color = person, label = person)) + 
  facet_wrap(~ length) + 
  xlab("Word position") + 
  ylab("Positional entropy") + 
  geom_pointrange(size = .25, aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_line(size = .25) + 
  theme_classic(base_size = 10) + 
  scale_color_ptol() + 
  theme(legend.position = "nones") + 
  geom_dl(aes(label = person), method = "last.points") 
```
bootstrap entropy slopes
```{r slope bootstrapping}

### 2019-04-19 ngrams/ngrams.Rmd
more plots for Monday

label_data <- data_frame(length = 8, language = "Spanish", gram_order = 6,
                         speaker_role = c("Adult", "Child"), empirical_entropy = c(9,10.25))

df %>% 
  filter(language %in% c("English", "Mandarin", "Spanish"), gram == "bigram", length %in% c(4, 6, 8)) %>%
  ggplot(aes(x = gram_order, y = empirical_entropy, color = speaker_role, label = speaker_role)) + 
  facet_grid(language ~ length, scales = "free") + 
  xlab("Gram position") + 
  ylab("Positional entropy") + 
  geom_pointrange(size = .25, aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_line(size = .25) + 
  theme_classic(base_size = 10) + 
  scale_color_ptol() + 
  theme(legend.position = "nones") + 
  geom_text(data = label_data)

>>>>

label_data <- data_frame(length = 9, language = "Spanish", gram_order = 6,
                         speaker_role = c("Adult", "Child"), empirical_entropy = c(9.25,10.25))

df %>% 
  filter(language %in% c("English", "Mandarin", "Spanish"), gram == "trigram", length %in% c(5, 7, 9)) %>%
  ggplot(aes(x = gram_order, y = empirical_entropy, color = speaker_role, label = speaker_role)) + 
  facet_grid(language ~ length, scales = "free") + 
  xlab("Gram position") + 
  ylab("Positional entropy") + 
  geom_pointrange(size = .25, aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_line(size = .25) + 
  theme_classic(base_size = 10) + 
  scale_color_ptol() + 
  theme(legend.position = "nones") + 
  geom_text(data = label_data)
